---
title: "DataVizProject"
author: "Huan LE, Mael-Antoine GNANOU, Otmane M'BIDA"
date: "22 avril 2019"
output:
  html_document:
    toc: TRUE
    code_folding: "hide"
    number_sections: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, fig.align='center')
```

# DataViz Project : Correlation between the 2018 World Cup and depression

We would like to know if there is a correlation between major sport events and depression within the winning country. We have chosen the 2018 World Cup and the country of France aka The Champions.

We got the data from Google Trends.

## Loading libaries

```{r}
library(ggplot2)
library(dplyr)
```

## Loading data

We host the data file on Github.

```{r loading}
data <- read.csv("https://raw.githubusercontent.com/huanlebui/DataVizProject/master/data.csv")

data$week <- as.Date(data$week)

```

## A first look into the data

We actually had two


```{r}
head(data)
```

## Nope

```{r}
data %>%
  ggplot( aes(x=week) ) +
    geom_line( aes(y = depression), color = "red" ) +
    geom_line( aes(y = cdm), color ="blue" )

```
