---
title: "DataViz Project : Correlation between the 2018 FIFA World Cup and depression"
author: "[Huan LE, Mael-Antoine GNANOU, Otmane M'BIDA](https://www.youtube.com/watch?v=dQw4w9WgXcQ)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  epuRate::PCTG:
    toc: TRUE
    code: "show"
    number_sections: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, fig.align='center')
# You need these libraries to run this template:
library(rmarkdown)    # install.packages("rmarkdown") 
library(epuRate)      # devtools::install_github("holtzy/epuRate", force=TRUE)
```

<br><br><br><br>

>We would like to know if there is a correlation between **major sport events** and **depression** within the winning country. We have chosen the 2018 FIFA World Cup and the country of France aka *le pays des Champions du Monde*.

>...and we got the data from Google Trends.


# Loading libraries
***
We will only need `ggplot2` and `dplyr`.

```{r}
library(ggplot2)
library(dplyr)
```




# Loading data
***
We host the data file on our Github.

```{r}
data <- read.csv("https://raw.githubusercontent.com/huanlebui/DataVizProject/master/data.csv")

data$week <- as.Date(data$week)

```



# A quick look into the data
***
We actually had two seperate CSV files so we merged them into one. Under the `depression` and `cdm` attributes we have the trending levels of the keywords *depression* (in terms of search queries) and *coupe du monde* (in terms of occurence in newsfeeds) respectively, throughout the year of 2018 in France.

```{r}
head(data)
```



# A primitive line chart
***
Let's look at the trending of the two keywords in 2018.

```{r}
data %>%
  ggplot( aes(x=week) ) +
    geom_line( aes(y = depression), color = "red" ) +
    geom_line( aes(y = cdm), color ="blue" )

```


We can observe a slight decrease during a relatively long period of time for the keyword *depression* around the month of July. And of course we can easily notice the obvious skyrocketing keyword *coupe du monde* between June and July.
